Data Preparation

### 2019-01-10 Data Preparation.Rmd

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which the course was taken as well as the calendar year.

The data we will be using was provided in two documents with the same format. We import them, merge them and remove duplicate rows.

>>>>

```{r import corpus_manuals, cache = TRUE}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                         readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `d_transcripts` contains the transcripts information of students as was provided. It has 40 columns, and rows correspond to a type of grade (e.g. final grade, attendance) per student per course per time they took it.
